---
title: "Heatseek NYC DB - Analysis Script"
author: "Jolene Lim"
date: "15 November 2019"
output: html_document
---

# Setup
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Load Data
```{r, message = FALSE}
hs = read_csv("data/heatseek_geocoded.csv")
complaints = read_csv("data/heatseek_complaints.csv")
violations = read_csv("data/heatseek_violations.csv")
```

```{r}
users = hs %>%
  group_by(user_id, address, zip_code, apartment) %>%
  summarize(n_violations = sum(violation)) %>%
  filter(!is.na(user_id))
```

```{r}
filter(users, n_violations > 1000)
```

# COMPLAINTS
## Question: How many users with violations (recorded by the sensor) filed a complaint in 2019?
```{r}
complaints_2019 = complaints %>%
  filter(str_detect(ReceivedDate, "2019"))

users_who_filed_2019 = unique(complaints_2019$user_id)

users = users %>%
  mutate(faced_violation = n_violations > 1) %>%
  mutate(faced_violation = factor(faced_violation, 
                                  levels = c(TRUE, FALSE),
                                  labels = c("Faced Violation", "Did Not Face Violation"))) %>%
  mutate(filed_complaint = user_id %in% users_who_filed_2019) %>%
  mutate(filed_complaint = factor(filed_complaint, 
                                  levels = c(TRUE, FALSE),
                                  labels = c("Filed Complaint", "Did Not File Complaint")))
```

```{r}
table(users$faced_violation, users$filed_complaint)
```

```{r}
ggplot(users, aes(x = filed_complaint, y = n_violations, color = as.factor(faced_violation))) +
  geom_jitter(width = 0.2) +
  labs(title = "Whether Users Filed Complaint and the Number of Violations They Faced",
       x = "Complaint Status",
       y = "Number of Violations") +
  scale_color_discrete(name = "Sensor Recorded Violation") +
  theme_minimal()
```

```{r}
n_complaints = complaints_2019 %>%
  group_by(user_id) %>%
  summarize(n_complaints = n())

users = left_join(users, n_complaints) %>%
  mutate(n_complaints = ifelse(is.na(n_complaints), 0, n_complaints))
```

```{r}
ggplot(users, aes(x = n_violations, y = n_complaints, color = filed_complaint)) +
  geom_point() +
  labs(title = "Number of Violations Recorded by Sensor v. Number of NYCDB Complaints",
       x = "Number of Violations Recorded by Sensor",
       y = "Number of NYCDB Complaints") +
  scale_color_discrete(name = "Whether User Filed Complaint") +
  theme_bw()

```

## Question: For those who did file complaints, were they users who did not file complaints in the last 2 years?
I.e., did the sensors motivate them to file a complaint? 

```{r}
users_who_filed = unique(complaints$user_id)

sum(!(users_who_filed_2019 %in% users_who_filed))
```

There are no such users.

# VIOLATIONS
## Question: How many users with violations (recorded by the sensor) eventually ended up as a violation case in 2019?
Note: Violations count both open and closed

```{r}
violations_2019 = violations %>%
  filter(str_detect(NOVIssuedDate, "2019"))

users_who_filedv_2019 = unique(violations_2019$user_id)

users = users %>%
  mutate(filed_violation = user_id %in% users_who_filedv_2019) %>%
  mutate(filed_violation = factor(filed_violation, 
                                  levels = c(TRUE, FALSE),
                                  labels = c("Filed Violation", "Did Not File Violation")))
```

```{r}
table(users$faced_violation, users$filed_violation)
```

```{r}
ggplot(users, aes(x = filed_violation, y = n_violations, color = faced_violation)) +
  geom_jitter(width = 0.2) +
  labs(title = "Whether Users Filed Violation and the Number of Violations They Faced",
       x = "Violation Status",
       y = "Number of Violations (Detected by Sensor)") +
  scale_color_discrete(name = "Sensor Recorded Violation") +
  theme_minimal()
```

```{r}
n_dbviolations = violations_2019 %>%
  group_by(user_id) %>%
  summarize(n_dbviolations = n())

users = left_join(users, n_dbviolations) %>%
  mutate(n_dbviolations = ifelse(is.na(n_dbviolations), 0, n_dbviolations))
```

```{r}
ggplot(users, aes(x = n_violations, y = n_dbviolations, color = filed_violation)) +
  geom_point() +
  labs(title = "Number of Violations Recorded by Sensor v. Number of NYCDB Violations",
       x = "Number of Violations Recorded by Sensor",
       y = "Number of NYCDB Violations") +
  scale_color_discrete(name = "Whether User Filed 311 Violation") +
  theme_bw()
```
