---
title: "Heatseek NYC DB - Cleaning Script"
author: "Jolene Lim"
date: "13 November 2019"
output: html_document
---
# Setup
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

# Load Heatseek Data
```{r, message = FALSE}
df = read_csv("data/heatseek_geocoded.csv", progress = FALSE)
```

```{r}
# create users df which only contains unique users, sum of the violations, and has house number and street extracted
users = df %>%
  group_by(user_id, address, zip_code, apartment) %>%
  summarize(n_violations = sum(violation)) %>%
  filter(!is.na(user_id)) %>%
  mutate(house_no = str_extract(address, "^(\\S)+(?=\\s)"))

# clean street names to format in NYC DB
street = str_split(users$address, pattern = " ") %>%
  map_chr(function(x) str_c(x[-1], collapse = " ")) %>%
  str_to_upper() %>%
  str_replace("^E ", "EAST ") %>%
  str_replace("^W ", "WEST ") %>%
  str_replace("(?<=[0-9])TH ", " ") %>%
  str_replace("(?<=[0-9])RD ", " ") %>%
  str_replace(" ST(?![:alpha:])", " STREET")

# add clean street name to users
users$street = street
```

```{r}
zips = unique(users$zip_code)
```

# Load Complaint Data
```{r, message = FALSE}
# load complaint data, filter for those with zip codes matching our users
comp = read_csv("data/Housing_Maintenance_Code_Complaints.csv")

complaints = comp %>%
  filter(Zip %in% zips)
```

```{r}
# join by Apt No., Post Code and House Number
hs_complaints = left_join(users, complaints, by = c("zip_code" = "Zip", 
                                                    "apartment" = "Apartment",
                                                    "house_no" = "HouseNumber"))
```

At this point, hs_complaints has all types of complaints, not just those relating to heat. Further filter to those specific to heat.
Another NYC DB, has the complaint problems associated with each complaint ID. Use that to further filter.

```{r, message = FALSE}
# Load Complaint Problems
problems = read_csv("data/Complaint_Problems.csv", progress = FALSE)
```

```{r}
# filter for heat-related problems
problems = problems %>%
  select(ComplaintID, CodeID, Code) %>%
  filter(str_detect(Code, "NO HEAT"))
```

```{r}
complaint_ids = unique(problems$ComplaintID)
```

Finally, get `hs_complaints` relating to heat.
```{r}
hs_complaints = hs_complaints %>%
  filter(ComplaintID %in% complaint_ids)
```

Additional check that the street names match (since we did not join by streetname, on the off-chance that zip code, house number and apt matches, a complaint from a different street could be joined).
```{r, message = FALSE}
hs_complaints %>%
  filter(street != StreetName) %>%
  select(user_id, street, StreetName) %>%
  kable() %>% kable_styling() %>% scroll_box(height = "300px")
```
Quick scroll suggests they are the same, just a result of poor initial cleaning.

# Load Violations Data
```{r, message = FALSE, warning = FALSE}
violations = read_csv("data/Housing_Maintenance_Code_Violations.csv", progress = FALSE)

violations = filter(violations, Postcode %in% zips) %>%
  filter(str_detect(NOVDescription, "SECTION 27-2029"))
```

```{r}
hs_violations = inner_join(users, violations, by = c("zip_code" = "Postcode",
                                                    "house_no" = "HouseNumber",
                                                    "apartment" = "Apartment"))

hs_violations %>%
  select(user_id, address, zip_code, apartment, NOVDescription, InspectionDate) %>%
  kable() %>% kable_styling() %>% scroll_box(height = "300px")
```

Quick check for street names
```{r, message = FALSE}
hs_violations %>%
  filter(street != StreetName) %>%
  select(user_id, street, StreetName) %>%
  kable() %>% kable_styling()
```

# Export the complaints and violations records for users
```{r}
write_excel_csv(hs_complaints, "data/heatseek_complaints.csv")
write_excel_csv(hs_violations, "data/heatseek_violations.csv")
```